Draft_Application_Stochastic_Volatility

### 2021-07-17 Real Dataset SV.Rmd
corrections

    \end{pmatrix} \Big|\rho,\tau & \overset{i.i.d.}{\sim}  N_2(\mathbf{0},\mathbf{\Sigma}), \ \mathbf{\Sigma}=

@@

When specifying the parameters of a stochastic volatility model, one should clarify whether the series of observed financial returns is one of log returns or of percentage log returns. Indeed, let $y_t$ denote the returns at time $t$, so that a basic SV specification would prescribe $y_t|x_t\sim N(0,e^{x_t})$: clearly, for each period $t$, $e^{x_t}$ needs to be higher to replicate the observed \textit{percentage} log return rather than the observed log return. This implies that the latent volatility $x$ should fluctuate around higher values when using percentage log returns as $y_t$.
This feature, when adopting the aforementioned canonical SV model as defined in Kim et al. (1998), would be represented by a higher $\mu$. For example, as noted in Kastner (2019), daily log returns often have a variance of 0.0001 or less, which implies that $\mu$ should lie somewhere around $\ln(0.0001)\approx -9$; instead, when considering daily percentage log returns, one then has a variance of 1, so that $\mu=\ln(1)=0$. Note that when $\mu=0$, the canonical model boils down to the basic specification we employed on the simulated dataset, so that we prefer using percentage log returns for the 3 indices. In other terms, one might end up with the basic specification of the SV model when (roughly) calibrating the parameters of the canonical model on a wider set of financial returns.

Note that rescaling the log returns has analogous implications for the section in which we employ measures of realised volatility as a proxy for the latent volatility process.
Let us denote by $rv5_t$ the daily realised variance at time $t$, which we obtain from the \textit{rv5} series provided in the Oxford-Man database. Now, note that in a SV framework one should not directly compare $rv5_t$ to $x_t$, as $rv5_t$ can be rather seen as an estimate of the variance of the log returns at time $t$, \textit{i.e.} of $e^{x_t}$ in the SV model. Moreover, by construction of $rv5_t$,\footnote{Nota sulla formula, che considera returns, non returns in percentuale. Spiegare qui perchè possa avere senso paragonare questa varianza a quella dei log returns} the comparison should feature a SV model where the log returns did \textit{not} undergo the percentage transformation. Thus, in order to achieve a common scale with the percentage log returns, we need to multiply $rv5$ by $100^2$. To ease the interpretation and representation of the comparison between differently approximated filtering distributions, we finally take the square root of the rescaled $rv5$, so that we compare it to $e^{x_t/2}$ (\textit{In realtà detto così è poco preciso, perchè in realtà andiamo a confrontare con la trasformazione della media dello stato filtrato}).

>>>>

    \end{pmatrix} \Big|\rho,\tau & \overset{i.i.d.}{\sim}  N_2(\mathbf{0},\Sigma), \ \Sigma=

@@

When specifying the parameters of a stochastic volatility model, one should clarify whether the series of observed financial returns is one of log returns or of percentage log returns. Indeed, let $y_t$ denote the returns at time $t$, so that a basic SV specification would prescribe $y_t|x_t\sim N(0,e^{x_t})$: clearly, for each period $t$, $e^{x_t}$ needs to be higher to replicate the observed \textit{percentage} log return rather than the observed log return. This implies that the latent volatility $x$ should fluctuate around higher values when using percentage log returns as $y_t$.
This feature, when adopting the aforementioned canonical SV model as defined in Kim et al. (1998), would be represented by a higher $\mu$. For example, as noted in Kastner (2019), daily log returns often have a variance of 0.0001 or less, which implies that $\mu$ should lie somewhere around $\ln(0.0001)\approx -9$; instead, when considering daily percentage log returns, one then has a variance of 1, so that $\mu=\ln(1)=0$. In other terms, one might end up with a basic specification of the SV model when (roughly) calibrating the parameters of the canonical model on a wider set of financial returns.

Note that rescaling the log returns has analogous implications for the section in which we employ measures of realised volatility as a proxy for the latent volatility process.
Let us denote by $rv5_t$ the daily realised variance at time $t$, which we obtain from the \textit{rv5} series provided in the Oxford-Man database. Now, note that in a SV framework one should not directly compare $rv5_t$ to $x_t$, as $rv5_t$ can be rather seen as an estimate of the variance of the log returns at time $t$, \textit{i.e.} of $e^{x_t}$ in the SV model. Moreover, by construction of $rv5_t$,\footnote{Nota sulla formula, che considera returns, non returns in percentuale. Spiegare qui perchè possa avere senso paragonare questa varianza a quella dei log returns, come fa Guidolin} the comparison should feature a SV model where the log returns did \textit{not} undergo the percentage transformation. Thus, in order to achieve a common scale with the percentage log returns, we need to multiply $rv5$ by $100^2$. To ease the interpretation and representation of the comparison between differently approximated filtering distributions, we finally take the square root of the rescaled $rv5$, so that we compare it to $e^{x_t/2}$ (\textit{In realtà detto così è poco preciso, perchè in realtà andiamo a confrontare con la trasformazione della media dello stato filtrato}).
